---
title: "EXP1_QP2"
author: "Marie Tano"
date: "2023-06-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
## extract the BibTeX entry from the return value
x <- citation()
toBibtex(x)
```


# Loading Libraries
```{r}
library(dplyr)
library(tidyverse)
library(ggrepel)
library(lmerTest)
library(lme4)
source("helpers.R")
library(foreign) 
library(lavaan)
library(semPlot)


```

# Loading Dataset
```{r}
EXP1 = read.csv("./headlines_experiment-trials.csv", stringsAsFactors=T, fileEncoding="latin1")
EXP1

list_cops <- list("police officer", "sheriff","officers", "cops", "officer", "security guard", "state trooper", "cop", "police chief", "border patrol agent",  "police")
list_people <- list("nurse", "Fisherman", "teen","owner", "vandal", "superintendent", "community leader", "patient", "doctor", "father", "driver", "teacher", "protesters", "student", "club bouncer", "waiter", "mom", "neighbor", "husband", "wife", "man")

EXP1 <- EXP1 %>% 
  mutate(cop_people = ifelse(Agent %in% list_cops, "Cop", "Man"))
EXP1
```




##lavPredictY()
```{r}
EXP1_no_NA  <- na.omit(EXP1)
levels(EXP1_no_NA$police.trust) <- list('1' = 'Yes', '0' = 'No')
levels(EXP1_no_NA$police.honest) <- list('1' = 'Yes', '0' = 'No')
levels(EXP1_no_NA$police.rights) <- list('1' = 'Yes', '0' = 'No')
levels(EXP1_no_NA$police.listen) <- list('1' = 'Yes', '0' = 'No')
levels(EXP1_no_NA$political.party) <- list('5' = 'Democratic', '3' = 'Independent', '2' = 'Libertarian','4' = 'Green','1' = 'Republican')
levels(EXP1_no_NA$conservative) <- list('1' = '5', '2' = '4', '3' = '3','4' = '2', '5' = '1')

EXP1_no_NA$police.trust <- as.numeric(as.character(EXP1_no_NA$police.trust))
EXP1_no_NA$police.honest <- as.numeric(as.character(EXP1_no_NA$police.honest))
EXP1_no_NA$police.rights <- as.numeric(as.character(EXP1_no_NA$police.rights))
EXP1_no_NA$police.listen <- as.numeric(as.character(EXP1_no_NA$police.listen))
EXP1_no_NA$political.party <- as.numeric(as.character(EXP1_no_NA$political.party))
EXP1_no_NA$conservative <- as.numeric(as.character(EXP1_no_NA$conservative))
EXP1_no_NA$police.stop <- as.numeric(as.character(EXP1_no_NA$police.stop))

EXP1_no_NA.model <- ' 
  # latent variable definitions
      trust1 =~ police.trust + police.honest + police.rights + police.listen
      politicallean =~ conservative + political.party + police.stop

  # regressions
    trust1 ~ politicallean
    politicallean ~ trust1
    
  # residual correlations
    police.trust ~~ police.listen
    police.honest ~~ police.rights + police.listen
    police.rights ~~ police.stop
    police.listen ~~ police.stop
  '

EXP1_no_NA1.fit <- sem(EXP1_no_NA.model, data = EXP1_no_NA)
#EXP1_no_NA2.fit <- cfa(EXP1_no_NA.model, data=EXP1_no_NA)
summary(EXP1_no_NA1.fit, standardized=TRUE, fit.measures=TRUE)

predicted_values <- lavPredictY(EXP1_no_NA1.fit, ynames = c("police.trust", "police.honest", "police.rights", "police.listen"),
                 xnames = c("conservative", "political.party", "police.stop"))
semPaths(EXP1_no_NA1.fit, "std")
```
###composite reliability 
```{r}

sl <- standardizedSolution(EXP1_no_NA1.fit)
sl2 <- sl$est.std[sl$op == "=~"]
re <- 1 - sl2^2 #Compute residual variance of each item
cdl <- sum(sl2[1:4])^2 / (sum(sl2[1:4])^2 + sum(re[1:4])) #Compute composite reliability
cd2 <- sum(sl2[5:7])^2 / (sum(sl2[5:7])^2 + sum(re[5:7])) #Compute composite reliability
cdl
cd2
```



##lavPredict()
```{r}
EXP1_no_NA  <- na.omit(EXP1)
levels(EXP1_no_NA$police.trust) <- list('1' = 'Yes', '0' = 'No')
levels(EXP1_no_NA$police.honest) <- list('1' = 'Yes', '0' = 'No')
levels(EXP1_no_NA$police.rights) <- list('1' = 'Yes', '0' = 'No')
levels(EXP1_no_NA$police.listen) <- list('1' = 'Yes', '0' = 'No')
levels(EXP1_no_NA$political.party) <- list('5' = 'Democratic', '3' = 'Independent', '2' = 'Libertarian','4' = 'Green','1' = 'Republican')
levels(EXP1_no_NA$gender) <- list('NB' = 'Non-binary/Non-conforming', 'M' = 'Man', 'W' = 'Woman')

levels(EXP1_no_NA$conservative) <- list('1' = '5', '2' = '4', '3' = '3','4' = '2', '5' = '1')


EXP1_no_NA$police.trust <- as.numeric(as.character(EXP1_no_NA$police.trust))
EXP1_no_NA$police.honest <- as.numeric(as.character(EXP1_no_NA$police.honest))
EXP1_no_NA$police.rights <- as.numeric(as.character(EXP1_no_NA$police.rights))
EXP1_no_NA$police.listen <- as.numeric(as.character(EXP1_no_NA$police.listen))
EXP1_no_NA$political.party <- as.numeric(as.character(EXP1_no_NA$political.party))
EXP1_no_NA$conservative <- as.numeric(as.character(EXP1_no_NA$conservative))
EXP1_no_NA$police.stop <- as.numeric(as.character(EXP1_no_NA$police.stop))

EXP1_no_NA2.model <- ' 
  # latent variable definitions
      trust1 =~ police.trust + police.honest + police.rights + police.listen
      politicallean =~ conservative + political.party + police.stop
  '

EXP1_no_NA2.fit <- cfa(EXP1_no_NA2.model, data=EXP1_no_NA)
summary(EXP1_no_NA2.fit, standardized=TRUE, fit.measures=TRUE)

predicted_values <- lavPredict(EXP1_no_NA2.fit)
predicted_values <- as.data.frame(predicted_values)
leanings <- predicted_values[["politicallean"]]
trust <- predicted_values[["trust1"]]
semPaths(EXP1_no_NA2.fit, "std")
```


###composite reliability 
```{r}

sl2 <- standardizedSolution(EXP1_no_NA2.fit)
sl2
sl22 <- sl2$est.std[sl2$op == "=~"]
sl22 # factor loadings
re2 <- 1 - sl22^2 #Compute residual variance of each item
cdl2 <- sum(sl22[1:4])^2 / (sum(sl22[1:4])^2 + sum(re2[1:4])) #Compute composite reliability
cd22 <- sum(sl22[5:7])^2 / (sum(sl22[5:7])^2 + sum(re2[5:7])) #Compute composite reliability

cdl2 # residual variance of each item
cd22 # composite reliability for trust



```
# Sanity Checks
## compare who harmer is 
```{r}
Target_Harmers <- target_data %>% 
  filter(!tolower(target_data$Agent) %in% tolower(target_data$Harmer))
```


##trust vs political 
```{r}
correlation <- cor(EXP1$trust, EXP1$leanings)
correlation
EXP1 %>% 
  group_by(trust, leanings) %>%
  ggplot(aes(x = trust, y=leanings)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  labs(x="Trust Measure",y="Political leaning Measure")
```


# Demographics
## race, age, gender
```{r}

as.numeric(as.character(count_demo$count))
table_demo <- aggregate(count_demo$count, list(count_demo$race, count_demo$age, count_demo$political.party, count_demo$gender), sum)
colnames(table_demo)[1] = "Race"
colnames(table_demo)[2] = "Age"
colnames(table_demo)[3] = "Political"
colnames(table_demo)[4] = "Gender"
colnames(table_demo)[5] = "Count"
table_demo$Political <- as.factor(table_demo$Political)
levels(table_demo$Political) <- list('Democratic' = '5', 'Independent' =  '3', 'Libertarian' = '2','Green' = '4', 'Republican' = '1')
levels(table_demo$Race) <- list('Asian' = 'Asian / Pacific Islander', 'Black' =  'Black', 'White' = 'White','Mixed' = 'Mixed', 'Native' = 'American Indian or Alaskan Native', "Hispanic" = "Hispanic")


summary(table_demo$Race)
summary(table_demo$Age)
summary(table_demo$Political)
summary(table_demo$Gender)

table_demo  %>%
  group_by(Race, Age, Political,Gender)%>%
  summarise(Count) %>%
  arrange(Count)

table_demo %>% 
  group_by(Race, Political,Age,Gender) %>%
  summarise(Count) %>%
  arrange(Count)  %>%
  ggplot(aes(x = Gender, y=Count)) +
  geom_bar(aes(fill = Political), position="stack", stat = "identity") +
  facet_grid(Race~Age) + 
  labs(y="Count",x="Gender")


table_demo %>% 
  group_by(Race, Political,Age,Gender) %>%
  summarise(Count) %>%
  arrange(Count)  %>%
  ggplot(aes(x = Race, y=Count)) +
  geom_bar(aes(fill = Political), position="stack", stat = "identity") +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  facet_grid(~Gender) + 
  labs(y="Count",x="Race")


table_demo %>% 
  group_by(Race, Political,Age,Gender) %>%
  summarise(Count) %>%
  arrange(Count)  %>%
  ggplot(aes(x = Race, y=Count)) +
  geom_bar(aes(fill = Political), position="stack", stat = "identity") +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  facet_grid(~Age) + 
  labs(y="Count",x="Race")


table_demo %>% 
  group_by(Race, Political,Age,Gender) %>%
  summarise(Count) %>%
  arrange(Count)  %>%
  ggplot(aes(x = Gender, y=Count)) +
  geom_bar(aes(fill = Political), position="stack", stat = "identity") +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  facet_grid(~Age) + 
  labs(y="Count",x="Race")
```



## race x trust
```{r}
EXP1_no_NA %>% 
  group_by(trust, race, cop_people) %>%
  ggplot(aes(x = trust, y = race)) +
  geom_point()
```

## party x trust
```{r}
EXP1_no_NA %>% 
  group_by(trust, political.party, cop_people) %>%
  ggplot(aes(x = trust, y = political.party)) +
  geom_point()
```


##Blame

### race
```{r}
EXP1_no_NA %>% 
  group_by(trust, race, cop_people) %>%
  summarise(blame_mean = mean(Blame))  %>% 
  ggplot(aes(x = trust, y=blame_mean)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  facet_grid(cop_people~race) +
  labs(x="Trust Measure",y="Mean Blame Rating")
```



### political
```{r}
EXP1_no_NA %>% 
  group_by(trust, political.party, cop_people) %>%
  summarise(blame_mean = mean(Blame))  %>% 
  ggplot(aes(x = trust, y=blame_mean)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  facet_grid(cop_people~political.party) +
  labs(x="Trust Measure",y="Mean Blame Rating")
```


### gender
```{r}
EXP1_no_NA %>% 
  group_by(trust, gender, cop_people) %>%
  summarise(blame_mean = mean(Blame))  %>% 
  ggplot(aes(x = trust, y=blame_mean)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  facet_grid(cop_people~gender) +
  labs(x="Trust Measure",y="Mean Blame Rating")
```


#Target: Blame

##Linear Regression
### Big Model
```{r}
target_data <- EXP1 %>% filter(Type == "Target") 
big_model = lmer(target_data$Blame ~ Grammar*cop_people + (1+Grammar*cop_people|Stimulus) + 
(1+Grammar*cop_people|WorkerID), data = target_data)
summary(big_model)
```

###Trust + Big Model
```{r}
target_data <- EXP1 %>% filter(Type == "Target") 
politicallean <- predicted_values[["politicallean"]]
trust1 <- predicted_values[["trust1"]]
participant <- c(unique(target_data$WorkerID)) # save participant IDs 



#political leaning 
leanings <- c(politicallean) 
names(leanings) <- participant # mapID to vector of values

leaningsdf <- as.data.frame(leanings) # turn into data frame
leaningsdf$WorkerID = participant # save worker ID to data frame for trust 

EXP1$leanings <- EXP1$WorkerID # save worker ID to trust column 
EXP1$leanings <- as.factor(EXP1$leanings) # factor it up 

 EXP1$leanings = leaningsdf$leanings[na.omit(match(EXP1$leanings,leaningsdf$WorkerID))] #save trust to EXP1


#trust 
trusts <- c(trust1) 
names(trusts) <- participant # mapID to vector of values

trustsdf <- as.data.frame(trusts) # turn into data frame
trustsdf$WorkerID = participant # save worker ID to data frame for trust 

EXP1$trust <- EXP1$WorkerID # save worker ID to trust column 
EXP1$trust <- as.factor(EXP1$trust) # factor it up 

EXP1$trust = trustsdf$trusts[na.omit(match(EXP1$trust,trustsdf$WorkerID))] #save trust to EXP1

EXP1_no_NA  <- na.omit(EXP1)

target_data <- EXP1 %>% filter(Type == "Target") 
biger_model = lmer(target_data$Blame ~ Grammar*cop_people*trust + (1+Grammar*cop_people|Stimulus) + 
(1+Grammar*cop_people|WorkerID), data = target_data)
summary(biger_model)

```


##Plots

###Agent x Agentivity 
```{r mean blame rating as a function of agent identity (x-axis) and agentivity (fill color)}
EXP1 %>% 
  filter(Type == "Target")  %>% 
  group_by(cop_people, Grammar) %>%
  summarise(blame_mean = mean(Blame))  %>% 
  ggplot(aes(x = cop_people, y=blame_mean)) +
  geom_bar(aes(fill = Grammar), position="dodge", stat = "identity") +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  labs(y="Mean Blame Rating",x="Agent Identity")
```

###Trust
```{r}
EXP1 %>% 
  group_by(trust, Type) %>%
  summarise(blame_mean = mean(Blame))  %>% 
  ggplot(aes(x = trust, y=blame_mean)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  facet_wrap(~Type) +
  labs(x="Trust Measure",y="Mean Blame Rating")
```

```{r}
target_data %>% 
  group_by(trust, Grammar, cop_people) %>%
  summarise(blame_mean = mean(Blame))  %>% 
  ggplot(aes(x = trust, y=blame_mean)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  facet_grid(cop_people~Grammar) +
  labs(x="Trust Measure",y="Mean Blame Rating")
```



```{r}
target_data %>% 
  group_by(trust, cop_people) %>%
  summarise(blame_mean = mean(Blame))  %>% 
  ggplot(aes(x = trust, y=blame_mean)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  facet_wrap(~cop_people) +
  labs(x="Trust Measure",y="Mean Blame Rating")
```


# Control:Blame
##Linear Regression

### cop or people vs control
```{r}
EXP1cop <-filter(EXP1, !(EXP1$Type == "Target" & EXP1$cop_people == "Man"))
just_people <- EXP1 %>% filter(cop_people == "Man")

just_people_lm = lmer(just_people$Blame ~ Grammar*Type + (1+Grammar*Type|Stimulus) + 
(1+Grammar*Type|WorkerID), data = just_people)
summary(just_people_lm)

EXP1cop_lm = lmer(EXP1cop$Blame ~ Grammar*Type + (1+Grammar*Type|Stimulus) + 
(1+Grammar*Type|WorkerID), data = EXP1cop)
summary(EXP1cop_lm)


```




### Big Model
```{r}
big_model_both = lmer(EXP1$Blame ~ Grammar*Type + (1+Grammar*Type|Stimulus) + 
(1+Grammar*Type|WorkerID), data = EXP1)
summary(big_model_both)
```

### trust + Big Model
```{r}
big_model_trust = lmer(EXP1$Blame ~ Grammar*Type*trust + (1+Grammar*Type|Stimulus) + 
(1+Grammar*Type|WorkerID), data = EXP1)
summary(big_model_trust)
```
### trust vs cop vs people
```{r}
EXP1cop <-filter(EXP1, !(EXP1$Type == "Target" & EXP1$cop_people == "Man"))
just_people <- EXP1 %>% filter(cop_people == "Man")

trust_model_cop = lmer(EXP1cop$Blame ~ Grammar*Type*trust + (1+Grammar*Type|Stimulus) + 
(1+Grammar*Type|WorkerID), data = EXP1cop)
summary(trust_model_cop)


trust_model_people = lmer(just_people$Blame ~ Grammar*Type*trust + (1+Grammar*Type|Stimulus) + 
(1+Grammar*Type|WorkerID), data = just_people)
summary(trust_model_people)

```


##Plots
###Agentivity
```{r mean blame/responsibility rating as a function of agentivity}
EXP1 %>% 
  group_by(Grammar,Type) %>%
  summarise(blame_mean = mean(Blame))   %>% 
  ggplot(aes(x = Grammar, y=blame_mean)) +
  geom_bar(position="dodge", stat = "identity",fill = c("wheat", "saddlebrown", "darkgoldenrod", "lightsalmon4")) +
  scale_x_discrete(guide = guide_axis(n.dodge=3))+
  geom_errorbar(position = position_dodge(width = .09), aes(ymax = blame_mean + ci.high(blame_mean), ymin= blame_mean - ci.low(blame_mean)), width=0.25) +
      geom_errorbar(position = position_dodge(width = .09), aes(ymax = blame_mean + ci.high(blame_mean), ymin= blame_mean - ci.low(blame_mean)), width=0.25) +
  facet_wrap(~Type, nrow=1) +
  labs(y="Mean Blame Rating",x="Agentivity")
```

### Agent identity 
```{r mean blame rating as a function of agent identity (x-axis) and agentivity (fill color)}
EXP1 %>% 
  group_by(cop_people, Type) %>%
  summarise(blame_mean = mean(Blame))  %>% 
  ggplot(aes(x = cop_people, y=blame_mean)) +
  geom_bar(position="dodge", stat = "identity", fill = c("wheat", "saddlebrown", "darkgoldenrod")) +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
    geom_errorbar(position = position_dodge(width = .09), aes(ymax = blame_mean + ci.high(blame_mean), ymin= blame_mean - ci.low(blame_mean)), width=0.25) +
  facet_wrap(~Type, nrow=1, scales = "free") +
  labs(y="Mean Blame Rating",x="Agent Identity")
```


### Agent x Agentivity 
```{r mean blame rating as a function of agent identity (x-axis) and agentivity (fill color)}
EXP1 %>% 
  group_by(cop_people, Grammar, Type) %>%
  summarise(blame_mean = mean(Blame))  %>% 
  ggplot(aes(x = cop_people, y=blame_mean)) +
  geom_bar(aes(fill = Grammar), position="dodge", stat = "identity") +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  facet_wrap(~Type, nrow=1, scales = "free") +
  labs(y="Mean Blame Rating",x="Agent Identity")
```






#Target: Responsibility
##Linear Regression
### Big Model
```{r}
target_data <- EXP1 %>% filter(Type == "Target") 
big_model_response = lmer(target_data$responsible ~ Grammar*cop_people + (1+Grammar*cop_people|Stimulus) + 
(1+Grammar*cop_people|WorkerID), data = target_data)
summary(big_model_response)
```

###Trust + Big Model
```{r}
target_data <- EXP1 %>% filter(Type == "Target") 
politicallean <- predicted_values[["politicallean"]]
trust1 <- predicted_values[["trust1"]]
participant <- c(unique(target_data$WorkerID)) # save participant IDs 



#political leaning 
leanings <- c(politicallean) 
names(leanings) <- participant # mapID to vector of values

leaningsdf <- as.data.frame(leanings) # turn into data frame
leaningsdf$WorkerID = participant # save worker ID to data frame for trust 

EXP1$leanings <- EXP1$WorkerID # save worker ID to trust column 
EXP1$leanings <- as.factor(EXP1$leanings) # factor it up 

 EXP1$leanings = leaningsdf$leanings[na.omit(match(EXP1$leanings,leaningsdf$WorkerID))] #save trust to EXP1


#trust 
trusts <- c(trust1) 
names(trusts) <- participant # mapID to vector of values

trustsdf <- as.data.frame(trusts) # turn into data frame
trustsdf$WorkerID = participant # save worker ID to data frame for trust 

EXP1$trust <- EXP1$WorkerID # save worker ID to trust column 
EXP1$trust <- as.factor(EXP1$trust) # factor it up 

EXP1$trust = trustsdf$trusts[na.omit(match(EXP1$trust,trustsdf$WorkerID))] #save trust to EXP1

target_data <- EXP1 %>% filter(Type == "Target") 
bigger_model_response = lmer(target_data$responsible ~ Grammar*cop_people*trust + (1+Grammar*cop_people|Stimulus) + 
(1+Grammar*cop_people|WorkerID), data = target_data)
summary(bigger_model_response)

```


##Plots
###Agent x Agentivity 
```{r mean responsible rating as a function of agent identity (x-axis) and agentivity (fill color)}
EXP1 %>% 
  filter(Type == "Target")  %>% 
  group_by(cop_people, Grammar) %>%
  summarise(responsible_mean = mean(responsible))  %>% 
  ggplot(aes(x = cop_people, y=responsible_mean)) +
  geom_bar(aes(fill = Grammar), position="dodge", stat = "identity") +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  labs(y="Mean Responsibility Rating",x="Agent Identity")
```

###Trust
```{r}
EXP1 %>% 
  group_by(trust, Type) %>%
  summarise(responsible_mean = mean(responsible))  %>% 
  ggplot(aes(x = trust, y=responsible_mean)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  facet_wrap(~Type) +
  labs(x="Trust Measure",y="Mean Responsibility Rating")
```

```{r}
target_data %>% 
  group_by(trust, Grammar, cop_people) %>%
  summarise(responsible_mean = mean(responsible))  %>% 
  ggplot(aes(x = trust, y=responsible_mean)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  facet_grid(cop_people~Grammar) +
  labs(x="Trust Measure",y="Mean Responsibility Rating")
```



```{r}
target_data %>% 
  group_by(trust, cop_people) %>%
  summarise(responsible_mean = mean(responsible))  %>% 
  ggplot(aes(x = trust, y=responsible_mean)) +
  geom_point(position="identity", stat = "identity") +
  geom_line() +
  geom_smooth(method = "lm", se = TRUE)  +
  facet_wrap(~cop_people) +
  labs(x="Trust Measure",y="Mean Responsibility Rating")
```


# Control:Responsibility

##Linear Regression
```{r}

```



##Plots
###Agentivity
```{r mean blame/responsibility rating as a function of agentivity}
EXP1 %>% 
  group_by(Grammar,Type) %>%
  summarise(responsible_mean = mean(responsible))   %>% 
  ggplot(aes(x = Grammar, y=responsible_mean)) +
  geom_bar(position="dodge", stat = "identity",fill = c("wheat", "saddlebrown", "darkgoldenrod", "lightsalmon4")) +
  scale_x_discrete(guide = guide_axis(n.dodge=3))+
  geom_errorbar(position = position_dodge(width = .09), aes(ymax = responsible_mean + ci.high(responsible_mean), ymin= responsible_mean - ci.low(responsible_mean)), width=0.25) +
  facet_wrap(~Type, nrow=1) +
  labs(y="Mean Responsibility Rating",x="Agentivity")
```

### Agent identity 
```{r mean blame rating as a function of agent identity (x-axis) and agentivity (fill color)}
EXP1 %>% 
  group_by(cop_people, Type) %>%
  summarise(responsible_mean = mean(responsible))  %>% 
  ggplot(aes(x = cop_people, y=responsible_mean)) +
  geom_bar(position="dodge", stat = "identity", fill = c("wheat", "saddlebrown", "darkgoldenrod")) +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  geom_errorbar(position = position_dodge(width = .09), aes(ymax = responsible_mean + ci.high(responsible_mean), ymin= responsible_mean - ci.low(responsible_mean)), width=0.25) +
  facet_wrap(~Type, nrow=1, scales = "free") +
  labs(y="Mean Responsibility Rating",x="Agent Identity")
```


### Agent x Agentivity 
```{r mean blame rating as a function of agent identity (x-axis) and agentivity (fill color)}
EXP1 %>% 
  group_by(cop_people, Grammar, Type) %>%
  summarise(responsible_mean = mean(responsible))  %>% 
  ggplot(aes(x = cop_people, y=responsible_mean)) +
  geom_bar(aes(fill = Grammar), position="dodge", stat = "identity") +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
    geom_errorbar(position = position_dodge(width = .09), aes(ymax = responsible_mean + ci.high(responsible_mean), ymin= responsible_mean - ci.low(responsible_mean)), width=0.25) +
  facet_wrap(~Type, nrow=1, scales = "free") +
  labs(y="Mean Responsibility Rating",x="Agent Identity")
```
